Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed

### 2012-12-01 paper.tex
added quick abstract

>>>>

\begin{abstract}
In this paper we give an overview of Discrete and Continuous Pursuit-Evasion problems, explaining their methodologies, information structures, and play scenarios. Subsequently, we attempt to combine their qualities together to create a real-time solution with Discrete strategic techniques.
\end{abstract}
